%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for Fiscal Sponsorship Agreement.

% This document was derived from the one used by the Software Conservancy.  Any
% issues with the current version should be reported to NumFOCUS, as the
% Software Conservancy is not responsible in any way for NumFOCUS' use.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[english,letterpaper,12pt]{article}

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{mathpazo}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage[verbose, twoside, dvips,
              paperwidth=8.5in, paperheight=11in,
              left=1in, right=1in, top=1.25in, bottom=.75in,
           ]{geometry}

\usepackage{color}
\definecolor{darkorange}{rgb}{.71,0.21,0.01}

%% Formatting
\pagestyle{fancy}

\lhead{}
\rhead{}
\chead{}

\cfoot{\thepage}
\lfoot{}
\rfoot{Initials: \rule{0.25\textwidth}{0.2mm}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%% Command definitions
% Define a \fix{...} command to easily highlight notes for ourselves during
% discussion.
\newcommand{\fix}[1]{
  \textcolor{darkorange} { \textbf{***FIX***} #1 } }

%% We declare a series of macros with placeholder names here, that will be
%% re-defined by each project in its own definitions file.  In principle, this
%% file should never be modified unless a project negotiates specific changes,
%% so any changes to this file will stand out as modifications to the substance
%% of the agreement and not simply filling in data.

%% Do NOT modify these definitions here!! They are meant only to declare the
%% commands for the first time, they will get their actual values in the
%% definitions file loaded below.

% Official name of the project, e.g. ``NumPy''
\newcommand{\project}{\textbf{PROJECT NAME}}

% All the names of the contributors of the project which will sign the document
% Every name listed here will also have to be listed in the final signature
% section
\newcommand{\contributors}{\textbf{CONTRIBUTOR-NAMES}}

% Name given to the signatories group, such as ``NumPy developers''
\newcommand{\signatories}{\textbf{SIGNATORIES}}

% Name given to the fiscal management team for the project, e.g. ``NumPy fiscal
% team''
\newcommand{\fiscalteam}{\textbf{FISCAL-TEAM-NAME}}

% Size of the project's fiscal management team
\newcommand{\teamsize}{\textbf{3 or 5 members [Project MUST decide]}}

% Mailing address for the leadership body, can be the personal address
% of one of the members
\newcommand{\leadershipaddress}{\textbf{MAILING ADDRESS}}

% Date at which the agreement becomes enforceable
\newcommand{\agreementdate}{\textbf{DD day of MM, 20YY}}

% Signatures for contributors
\newcommand{\contributorsig}[1]{
By: \hspace{0.95em}\rule{0.50\textwidth}{0.2mm} \hfill{}Date: \rule{0.25\textwidth}{0.2mm}

\hspace{2.5em} #1

\vspace{2ex}
}

%% Load the actual values of the macro definitions for each project
\input{definitions}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\textsc{\Huge Fiscal Sponsorship Agreement}{\Huge {} } 
\par\end{center}

\bigskip{}

This Agreement is made by and between the NumFOCUS Foundation (``NumFOCUS'')
and \contributors{} (the ``\signatories{}'') on behalf of the project known as
\project{} (the ``Project'') (each, a ``Party''; together, ``the Parties'').
NumFOCUS is a Texas nonprofit public benefit corporation located in Austin,
Texas, which has received recognition of exemption from federal income tax under
Section 501(c)(3) of the Internal Revenue Code (IRC) and classification as a
public charity under IRC Sections 509(a)(1) and 170(b)(1)(A)(vi).

\textsc{Whereas:}

\begin{enumerate}[label=\Alph*.,ref=\S \Alph*]

\item NumFOCUS’ organizational purpose and charitable goal is to promote the
  use of accessible and reproducible computing in science and technology
  through educational programs, support of reproducible scientific research,
  and promotion of open-source software development, collaborative research
  tools and documentation.

\item The purpose of the Project is to produce, distribute, document, and
  improve software and/or documentation that can be freely copied, modified and
  redistributed, and for which modified versions can also be redistributed
  (``Open Source Software''), and to facilitate and organize its production,
  improvement and ease of use.

\item NumFOCUS desires to act as the fiscal sponsor of the Project beginning on
  the Effective Date (as defined below) to assist the Project in accomplishing
  its purpose, which NumFOCUS has determined will further NumFOCUS' charitable
  goals. The \signatories{} desire to manage the Project under the sponsorship
  of NumFOCUS.

\item NumFOCUS' Board of Directors has approved the establishment of a fund to
  receive donations of cash and other property earmarked for support of the
  Project and to make disbursements in furtherance of the Project's mission
  (the ``Project Fund''). Currently, the principal office of the Project is
  located at: \leadershipaddress{}.

\end{enumerate}

\medskip{}

\textsc{Now, therefore, the Parties hereby agree as follows:}

\begin{enumerate}[label=\arabic*.,ref=\S~\arabic*]
\item \textbf{Term of Agreement}. As of the Effective Date, the Project
joins NumFOCUS, which relationship will continue unless and until
terminated as set forth in \ref{Termination}. 
\item \textbf{Project Management and Activities}.


\begin{enumerate}[label=\alph*.,ref=\theenumi(\alph*)]

\item \textbf{The \fiscalteam{} Will Manage the Fiscal Interactions of the
    Project with NumFOCUS}. \label{ProjectManagement} Authority to manage the
  fiscal decisions made by the Project in regards to all funds held by NumFOCUS
  is delegated to the \fiscalteam{} as defined in \ref{Representation}.
  NumFOCUS will only intervene in the program activities to the extent the
  Project is not in compliance with \ref{OpenSourceSoftware} or
  \ref{CharitablePurpose} of this Agreement.

\item \textbf{The Project Will Be Open Source
  Software}. \label{OpenSourceSoftware} NumFOCUS and the \fiscalteam{}
  agree that any and all software and/or documentation distributed by the
  Project will be distributed solely as Open Source Software.  NumFOCUS retains
  the sole right to determine whether Project's software and/or documentation
  constitutes Open Source Software (as defined herein).
  
\item \textbf{Project Not An Agent Of NumFOCUS}. The \signatories{} hereby
  acknowledge that the Project and the \fiscalteam{} do not and shall not
  act as an agent for NumFOCUS unless specifically authorized in writing by
  NumFOCUS to do so.

\end{enumerate}

\item \textbf{Fees}.  In order to defray NumFOCUS' costs of administering the
  project's funds, NumFOCUS shall deduct an administrative charge equal to a
  percentage of any donation designated for purposes of the Project, plus any
  actual processing fees incurred by NumFOCUS for the processing of financial
  transactions (such as credit card processing fees, bank wires, foreing
  currency exchange costs, online payment system fees, etc.)  These fees are
  typically, but not necessarily, on the order of 3\%. The base percentage will
  be calculated based on the total amount donated to the project during any
  given year.  The schedule of such administrative charges is as follows:

\begin{enumerate}

\item Total less than \$150,000: 7\% + actual fees.

\item Total between \$150,000 and \$500,000: 6\% + actual fees.

\item Total between \$500,000 and \$1,000,000: 5\% + actual fees.

\item Total exceeding \$1,000,000: 4\% + actual fees.

\end{enumerate}


Notwithstanding the above, the \signatories{} agree that should NumFOCUS
be required to pay any taxes (including but not limited to sales taxes
and unrelated business taxable income) as the result of any activity
of the Project and/or activities undertaken by NumFOCUS on the
Project's behalf, such taxes shall be deducted from the Project Fund.

NumFOCUS will monitor any unrelated business taxable income and
may require the Project to cease activities generating such income
if the overall amounts exceed amounts permissible or prudent for NumFOCUS,
given NumFOCUS' tax exempt status.

\item \textbf{Project Fund/Variance Power}. Beginning on the Effective Date,
  NumFOCUS shall place all gifts, grants, contributions and other revenues
  received by NumFOCUS and identified with the Project into a Project Fund to
  be used for the sole benefit of the Project's mission as that mission may be
  defined by the \fiscalteam{} from time to time with the approval of
  NumFOCUS. The \fiscalteam{} will provide to NumFOCUS requests for
  disbursement of funds in accordance with the project mission. NumFOCUS
  retains the right to withhold disbursement to the project in the event that
  project activities violate the NumFOCUS charter.  Additionally, NumFOCUS
  retains the right to decline incoming funds on behalf of the project in any
  case where such action would also be in violation of NumFOCUS' charter.

  
\item \textbf{Project Fund Management / Performance of Charitable
  Purposes}. \label{CharitablePurpose} All of the assets received by NumFOCUS
  under the terms of this Agreement shall be devoted to the purposes of the
  Project, within the tax-exempt purposes of NumFOCUS. The \signatories{} agree
  not to use its funds or operate in any way which would jeopardize the
  tax-exempt status of NumFOCUS. No item of revenue shall be earmarked for use
  in any attempt to influence legislation within the meaning of IRC Section
  501(c)(3) and no agreement, oral or written, to that effect shall be made
  between NumFOCUS and any revenue source. NumFOCUS shall not use any portion
  of the assets to participate or intervene in any political campaign on behalf
  or in opposition to any candidate for public office, to induce or encourage
  violations of law or public policy, to cause any private inurement or
  improper private benefit to occur, nor to take any other action inconsistent
  with IRC Section 501(c)(3).

\item \textbf{Representation of the Project in
  NumFOCUS}. \label{Representation}The \signatories{}, each a signatory hereto,
  hereby establish and comprise the initial members of the \fiscalteam{} to
  represent the Project in its official communication with NumFOCUS.  The
  \signatories{} hereby acknowledge that the \fiscalteam{} will be subject
  to all terms of this Agreement.  On the Effective Date, the \signatories{}
  hereby transfer all rights, obligations and privileges of this Agreement over
  to the \fiscalteam{}.

  The \fiscalteam{} shall contain \teamsize{}, and shall designate a single
  ``Representative'' who will act as the point of contact with NumFOCUS for
  regular communications.  NumFOCUS reserves the right to request additional
  information from other members of the \fiscalteam{} beyond the
  Representative.

  The \fiscalteam{} has discretion on how to nominate and change its
  members, provided it notify NumFOCUS in writing of any changes made and a new
  copy of this agreement is signed by the new members at the time of change.

\item \textbf{Conflict of Interest of \fiscalteam{} members}. The \fiscalteam{}
  shall not consist of a majority of members who are employees of any one
  for-profit entity or have a significant financial interest in the same.
  Significant financial interest is defined as receiving income of at least
  \$5,000 annually, owning Stocks, Bonds, Stock Options or similar instruments
  with a market value of at least \$5,000, or representing at least 5\% of the
  total value of the for-profit entity.

  If two (2) or more members have a signifcant financial interest with the same
  for-profit entity or share an affiliation with a non-profit entity (such as
  working for the same University), such information must be declared in
  writing to NumFOCUS. If the NumFOCUS Board of Directors determines by a
  majority vote that a conflict of interest does exist, they may require the
  team to change the composition of its \fiscalteam{} within 30 days.

  If NumFOCUS identifies a conflict of interest that is not covered by the
  language above, NumFOCUS reserves the right to require the team to change the
  composition of its \fiscalteam{} within 30 days.

\item \textbf{Outstanding Liabilities}. The \signatories{} represent that any
  liabilities that may be outstanding in connection with the Project have been
  disclosed to NumFOCUS.

\item \textbf{Termination}. \label{Termination} The \fiscalteam{} or
  NumFOCUS may terminate this Agreement at any time subject to the following
  understandings:

\begin{enumerate}[label=\alph*.,ref=\theenumi(\arabic*)]

\item \textbf{Notice and Successor Search}. Either NumFOCUS or the
  \fiscalteam{} may terminate this Agreement on sixty (60) days' written
  notice to the other Party, so long as a Successor can be found that meets the
  following requirements (the ``Successor has Qualified''):


\begin{enumerate}[label=\roman*.,ref=\theenumi(\alph{enumii})(\roman*)]
  
\item the Successor is another nonprofit corporation which is tax-exempt under
  IRC Section 501(c)(3),
  
\item the Successor is not classified as a private foundation under Section
  509(a),
  
\item the Successor is willing and able to sponsor the Project, and,
  
\item the Successor has (a) communicated its willingness to sponsor the Project
  in writing to NumFOCUS and (b) sent a copy of its 501(c)(3) determination
  letter to NumFOCUS, and,
  
\item the Successor is approved in writing by both Parties by the end of the
  60-day period, such approval not to be unreasonably withheld.
  
\end{enumerate}

\item \textbf{Additional Search Periods}. If the Parties cannot agree on a
  Successor to sponsor the Project, the \fiscalteam{} shall have an
  additional 60 days to find a Successor willing and able to sponsor the
  Project. Any subsequent search periods of any length shall only be granted at
  NumFOCUS' written permission.

\item \textbf{Transfer to a Successor}. If a Successor has Qualified, the
  balance of assets in the Project Fund, together with any other assets held or
  liabilities incurred by NumFOCUS in connection with the Project, shall be
  transferred to the Successor within thirty (30) days of the approval of the
  Successor in writing by both Parties or any extension thereof, subject to the
  approval of any third parties that may be required.

\item \textbf{Termination Without a Successor}. If no Successor is found,
  NumFOCUS may dispose of Project assets and liabilities in any manner
  consistent with applicable tax and charitable trust laws.

\item \textbf{\signatories{}' Right to Terminate.}  The \signatories{} hereby
  acknowledge that they will relinquish any rights to terminate separate from
  the \fiscalteam{} as of the Effective Date.

\end{enumerate}

\item \textbf{Miscellaneous}. Each provision of this Agreement shall be
  separately enforceable, and the invalidity of one provision shall not affect
  the validity or enforceability of any other provision.  This Agreement shall
  be interpreted and construed in accordance with the laws of the State of
  Texas. This Agreement constitutes the only agreement, and supersedes all
  prior agreements and understandings, both written and oral, among the Parties
  with respect to the subject matter hereof.

\item \textbf{Amendments. }This Agreement may not be amended or modified,
  except in writing and signed by both NumFOCUS and the entirety of
  \fiscalteam{}.

\item \textbf{Counterparts / Facsimile}. This Agreement may be executed in two
  or more counterparts, each of which shall constitute an original, but all of
  which, when together, shall constitute but one and the same instrument, and
  shall become effective when one or more counterparts have been signed by each
  Party hereto and delivered to the other Party.  In lieu of the original, a
  facsimile transmission or copy of the original shall be as effective and
  enforceable as the original.

\end{enumerate}

\vfill{}


\textsc{In witness whereof}, the Parties have executed this Fiscal
Sponsorship Agreement effective on the \agreementdate{} (the
``Effective Date'').

\vspace{3em}


By: \hspace{0.95em}\rule{0.50\textwidth}{0.2mm} \hfill{}Date: \rule{0.25\textwidth}{0.2mm}

\hspace{2.5em} \textsc{The NumFOCUS Foundation.}

\hspace{2.5em} Travis E. Oliphant, Chairman.  \\[6ex]

\vspace{2ex}

%% Pull in the actual signatures from the project contributors
\input{signatures}

\end{document}
